SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-31 docs/questioning.tex
policy enforcement draft ready

There is already a survey on mitigating
software vulnerabilities in general~\cite{SZ12}.
The scope of that research is pretty wide and leaves
out many approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned in the previous paragraph.
In our research we focus on the top
{\sc tba} systems that counter application attacks,
in terms of citations.

@@

A recent class of {\sc cia}s involve dynamic languages like
JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
injection attacks, in particular, make up a large subset of dynamic
language-driven attacks. Such attacks are manifested when a web
application accepts and redisplays data of uncertain origin without
appropriate validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}. JavaScript injection
attacks are considered as a critical issue in web application security
mainly because they are associated with major vulnerabilities such as:
{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{LZRL09} and
Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
In many cases {\sc xss} attacks involve the injection of
both {\sc html} and JavaScript code.

@@

\begin{figure*} [ht]
\begin{center}
\leavevmode
\includegraphics[scale=0.62]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

@@

%{\it j{\sc csrf}}~\cite{PS11}.

% controlling information flows: {\sc soma}~\cite{OWVS08}
% and Noxes~\cite{KKVJ06,KJKV09} (the client defines policies).

@@

  \multirow{12}{*}{Policy Enforcement}

@@

  &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\

@@

@@

  &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\

>>>>

There is already a survey on mitigating
software vulnerabilities in general~\cite{SZ12}.
The scope of that research is pretty wide and leaves
out many approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned in the previous paragraph.

In our research we focus on the top
{\sc tba} systems that and are presented
in publications cited more than twenty times.
For the sake of our study, we choose
to make some exceptions and include some latest mechanisms
that were presented in top security conferences even if
the corresponding publications have been cited less than
twenty times.

@@

A recent class of {\sc cia}s involve dynamic languages like
JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
injection attacks, in particular, make up a large subset of dynamic
language-driven attacks. Such attacks are manifested when a web
application accepts and redisplays data of uncertain origin without
appropriate validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}. JavaScript injection
attacks are considered as a critical issue in web application security
mainly because they are associated with major vulnerabilities such as:
{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{BJM08,LZRL09} and
Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
In many cases {\sc xss} attacks involve the injection of
both {\sc html} and JavaScript code.

@@

\begin{figure*} [ht]
\begin{center}
\leavevmode
\includegraphics[scale=0.65]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

@@

Policy enforcement mechanisms that detect {\sc csrf}
attacks are usually implemented in the form of a
server-side proxy (locus {\sc y})
interposing on the client-server communication, and modifying
it. {\it NoForge}~\cite{JKK06a}
parses the {\sc html} server responses
and adds a token to every {\sc url} referring to this
server. Then it associates the token with the cookie
representing the session {\sc id} for the application.
When a request is received, the mechanism checks
if the request contains the token related
to the session {\sc id}. A disadvantage of NoForge
is that {\sc html} that is dynamically created within
the browser will not include the token.
Thus, sites that create their {\sc html} on the client
will remain vulnerable. In addition, it does not
support cross-origin requests.
{\it j{\sc csrf}}~\cite{PS11}
has a very similar functionality and meanwhile
addresses the above problems.
Finally, {\it CsFire}~\cite{DDHPJ10}
examines cross-domain interactions,
to design a cross-domain policy.
The policy is based on the concept of a relaxed
same-origin policy that allows communication between
sub-domains of the same registered domain.

Most of the aforementioned frameworks, involve
several deployment issues since they
require significant source modifications by the web
developers in order to introduce their policies.

@@

  \multirow{11}{*}{Policy Enforcement}

@@

  % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\

@@

 We need to mention that there are mechanisms that
 do not need to be established purely through testing
 Since they provide systematic arguments as to why
 the design is secure against attacks.

@@

  % &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
